Fixing Vulnerabilities Hinders Maintainability

### 2019-02-04 paper/ICPC19/icpc19.tex
cleaning fixes

Every SSL/TLS connection begins with a handshake which is responsible by the
negotiation between two parties. DTLS provides a mechanism for fragmenting a
handshake message over a number of packets, each of which can be transmitted
separately. In the example (Listing~\ref{lst:vuln}), all functions receive as
input the SSL session, \texttt{s}. In the \texttt{dtls1\_reassemble\_fragment}
function the size of the fragment \texttt{msg\_hdr-$>$frag\_off+frag\_len} is
checked against the handshake message size \texttt{msg\_hdr->msg\_len} (line
$13$) and then against the maximum size allowed in a DTLS handshake message for \texttt{s} (line $16$-$21$)\Rui{DTLS1 for s?}\Sof{Better?}. However, it is not verified if \texttt{msg\_hdr->msg\_len} is lower than the size allowed by DTLS. \Rui{$<$- does not parse}\Sof{Better?} Thus, in line
$37$, when \texttt{msg\_len} is allocated to the fragment buffer, more memory
than the allowed might be allocated. According to the commit message, $10$
handshake messages are allowed per DTLS connection. Hence, a remote attacker
could leverage this issue to trigger memory allocations corresponding to large
length values and lead the system to memory exhaustion that could end in a DoS
attack. The code changes performed to fix the vulnerability were the following:

~\ref{lst:func1} \texttt{dtls1\_max\_handshake\_message\_len} function was
inserted to return the maximum number of bytes allowed in a DTLS
handshake message for \texttt{s}. The minimum is $16$KB but it might be greater if the maximum certificate list size requires it. \Rui{$<$- does not parse}\Sof{Better?} More
specifically, it checks if the maximum certificate list size
(\texttt{s-$>$max\_cert\_list}) requires more length than the maximum length
(\texttt{max\_len}). If that condition holds, the function returns the size of
the certificate list, otherwise, it returns the maximum length. This function
replaces lines $18$-$21$.

@@

\begin{itemize}
    \item \Sof{Cases added, check it out}\textbf{Using Components with Known Vulnerabilities (21 cases).} The majority of
    software produced today integrates several components, such as libraries and
    frameworks, which may affect the software if developers use vulnerable
    versions - usually known and disclosed somewhere on the Internet.
    \textit{Based on the OWASP Top $10$ of $2017$.}

@@

One of the guidelines with which the project does not comply is the one presented in the report (cf. Figure~\ref{fig:bchrep}): \emph{Write Simple Units of Code}. SIG defines \emph{Units} as the smallest groups of code that can be maintained and executed independently~\cite{Visser:2016:OREILLY} (e.g., methods and constructors in Java). BCH reports

>>>>

Every SSL/TLS connection begins with a handshake which is responsible by the
negotiation between two parties. DTLS provides a mechanism for fragmenting a
handshake message over a number of packets, each of which can be transmitted
separately. In the example (Listing~\ref{lst:vuln}), all functions receive as
input the SSL session, \texttt{s}. In the \texttt{dtls1\_reassemble\_fragment}
function the size of the fragment \texttt{msg\_hdr-$>$frag\_off+frag\_len} is
checked against the handshake message size \texttt{msg\_hdr->msg\_len} (line
$13$) and then against the maximum size allowed in a DTLS handshake message for \texttt{s} (line $16$-$21$). However, it is not verified if \texttt{msg\_hdr->msg\_len} is lower than the size allowed by DTLS. Thus, in line
$37$, when \texttt{msg\_len} is allocated to the fragment buffer, more memory
than the allowed might be allocated. According to the commit message, $10$
handshake messages are allowed per DTLS connection. Hence, a remote attacker
could leverage this issue to trigger memory allocations corresponding to large
length values and lead the system to memory exhaustion that could end in a DoS
attack. The code changes performed to fix the vulnerability were the following:

~\ref{lst:func1} \texttt{dtls1\_max\_handshake\_message\_len} function was
inserted to return the maximum number of bytes allowed in a DTLS
handshake message for \texttt{s}. The minimum is $16$KB but it might be greater if the maximum certificate list size requires it. More
specifically, it checks if the maximum certificate list size
(\texttt{s-$>$max\_cert\_list}) requires more length than the maximum length
(\texttt{max\_len}). If that condition holds, the function returns the size of
the certificate list, otherwise, it returns the maximum length. This function
replaces lines $18$-$21$.

@@

\begin{itemize}
    \item \textbf{Using Components with Known Vulnerabilities (21 cases).} The majority of
    software produced today integrates several components, such as libraries and
    frameworks, which may affect the software if developers use vulnerable
    versions - usually known and disclosed somewhere on the Internet.
    \textit{Based on the OWASP Top $10$ of $2017$.}

@@

One of the guidelines with which the project does not comply is the one presented in the report (cf. Figure~\ref{fig:bchrep}): \emph{Write Simple Units of Code}. SIG defines \emph{Units} as the smallest groups of code that can be maintained and executed independently~\cite{Visser:2016:OREILLY} (e.g., methods and constructors in Java). BCH evaluates this guideline based on the number
